Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-19 prop_iop.tex
prop_iop.tex \section{Why Empty Core?} Updating...

One possibility is that the definition of quantum convexity is too
weak to guarantee a convex quantum interval-valued probability measure
having a non-empty core. On one hand, strengthening equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
to non-commuting projectors~$P_{0}$ and $P_{1}$ is unlikely to
success because the product of non-commuting projectors is not a projector.
On the other hand, strengthening equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
among commuting projectors cannot guarantee a non-empty core as well
if we follow what people strengthen convexity classically. Equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
classically is a special case of 
\begin{equation}
\bar{\mu}'\left(\bigcup_{i=1}^{N}E_{i}\right)+\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is odd}}\bar{\mu}'\left(\bigcap_{i\in I}E_{i}\right)\subseteq\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is even}}\bar{\mu}'\left(\bigcap_{i\in I}E_{i}\right)\label{eq:Dempster-Shafer-game}
\end{equation}
when $N=2$, where $\bar{\mu}'$ is a classical interval-valued probability
measure. If $\bar{\mu}'$ satisfies equation~(\ref{eq:Dempster-Shafer-game})
for all set of event~$\left\{ E_{i}\right\} _{i=1}^{N}\subseteq2^{\Omega}$,
then the left-end point of $\bar{\mu}'$ is called a Dempster-Shafer
belief function. It is reasonable to call a quantum interval-valued
probability~$\bar{\mu}$ Dempster-Shafer if $\bar{\mu}$ satisfies
\begin{equation}
\bar{\mu}\left(\bigvee_{i=1}^{N}P_{i}\right)+\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is odd}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\subseteq\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is even}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game-quantum}
\end{equation}
for all set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events$.
However, the quantum interval-valued probability measure in example~\ref{ex:three-dimensional-three-value}
is Dempster-Shafer and has an empty core. In summary, it is unlikely
to guarantee a non-empty core by strengthening convexity.

\subsection{Restricting the Event Space}

Since the discover of Heisenberg's uncertainty principle~\cite{Heisenberg1983,peres1995quantum,544199,Griffiths2003,Jaeger2007},
non-commuting observables is considered as one of the reason why quantum
theory is different from the classical one. In another word, the uncertainty
principle would not be observed if we could only access commuting
observables. This is also true for a quantum interval-valued probability
measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$. If we restrict
our event space~$\events$ to a mutually commuting subspace~$\events'$,
as proved in theorem~\ref{thm:sub-event-space}, the restricted $\bar{\mu}|_{\events'}$
is essentially a classical interval-valued probability measure. Furthermore,
if $\bar{\mu}$ is convex, then $\bar{\mu}|_{\events'}$ will be convex,
and have a non-empty core classically.

>>>>

One possibility is that the definition of quantum convexity is too
weak to guarantee a convex quantum interval-valued probability measure
having a non-empty core. On one hand, strengthening equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
to non-commuting projectors~$P_{0}$ and $P_{1}$ is unlikely to
success because the product of non-commuting projectors is not a projector.
On the other hand, strengthening equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
among commuting projectors cannot guarantee a non-empty core as well
if we follow what people strengthen convexity classically. Equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
classically is a special case of 
\begin{equation}
\bar{\mu}'\left(\bigcup_{i=1}^{N}E_{i}\right)+\sum_{{{\scriptstyle I\subseteq\left\{ 1,\ldots,N\right\} }\atop {\scriptstyle \left|I\right|\textrm{ is odd}}}}\bar{\mu}'\left(\bigcap_{i\in I}E_{i}\right)\subseteq\sum_{{{\scriptstyle I\subseteq\left\{ 1,\ldots,N\right\} }\atop {\scriptstyle \left|I\right|\textrm{ is even}}}}\bar{\mu}'\left(\bigcap_{i\in I}E_{i}\right)\label{eq:Dempster-Shafer-game}
\end{equation}
when $N=2$, where $\bar{\mu}'$ is a classical interval-valued probability
measure. If $\bar{\mu}'$ satisfies equation~(\ref{eq:Dempster-Shafer-game})
for all set of event~$\left\{ E_{i}\right\} _{i=1}^{N}\subseteq2^{\Omega}$,
then the left-end point of $\bar{\mu}'$ is called a Dempster-Shafer
belief function. It is reasonable to call a quantum interval-valued
probability~$\bar{\mu}$ Dempster-Shafer if $\bar{\mu}$ satisfies
\begin{equation}
\bar{\mu}\left(\bigvee_{i=1}^{N}P_{i}\right)+\sum_{{{\scriptstyle I\subseteq\left\{ 1,\ldots,N\right\} }\atop {\scriptstyle \left|I\right|\textrm{ is odd}}}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\subseteq\sum_{{{\scriptstyle I\subseteq\left\{ 1,\ldots,N\right\} }\atop {\scriptstyle \left|I\right|\textrm{ is even}}}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game-quantum}
\end{equation}
for all set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events$.
However, the quantum interval-valued probability measure in example~\ref{ex:three-dimensional-three-value}
is Dempster-Shafer and has an empty core. In summary, it is unlikely
to guarantee a non-empty core by strengthening convexity.

\subsection{Commuting Sub-Event Space}

Since the discover of Heisenberg's uncertainty principle~\cite{Heisenberg1983,peres1995quantum,544199,Griffiths2003,Jaeger2007},
the existence of non-commuting observables is one of the reason why
quantum theory is different from the classical theory. In another
word, the uncertainty principle would not be observed if we could
only access commuting observables. This is also true for a quantum
interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$.
If we restrict our event space~$\events$ to a mutually commuting
subspace~$\events'$, as proved in theorem~\ref{thm:sub-event-space},
the restricted $\bar{\mu}|_{\events'}$ is essentially a classical
interval-valued probability measure. Furthermore, if $\bar{\mu}$
is convex, then $\bar{\mu}|_{\events'}$ will be convex, and have
a non-empty core classically.
